The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Add reference to figure in implementation

\subsection{Interactive game}
The interactive game is coded using QML, and displays a main background image on
top of which items (animals, humans and objects) can be moved. 
The children can also use a drawing mode to
create coloured strokes on a layer between the background and the items, which adds another layer of unconstrained interaction to the game
(eg. Figure~\ref{fig|sandbox}. The game exposes the image of the background,
the drawings, and the positions of the objects as a TF frame.

\subsection{Sensors}
Two RGB-D cameras are mounted at fixed positions on the Sandtray frame, each facing a child. This fixed position of the cameras allows the extraction of social features 
such as head pose, eye gaze, pointing and body posture, all described in a general
coordinate system available to each software node. In addition to the image, the cameras
posses a microphone to record the auditory aspect of the interaction.

@@

\subsection{Robot Control}
As stated in section~\ref{ssec|CRI}, a robot can act as play partner instead of one of the
children. This robot can either be autonomous selecting actions based on the
inputs provided by the sensors and the game or be controlled by a human in a
Wizard of Oz fashion.

\paragraph{Autonomous} The current implementation exposes a large number of
information on the game and the state of the child that can be used in the robot
controller. The position of every item is exposed as a TF frame, the background
is segmented in zones of identical colors, social element of the state the
interaction are collected through the RGBD camera and the microphone facing the
child. As visible on Figures~\ref{fig|freeplay} and \ref{fig|rviz}, the camera
covers the head of the child as well as most of the upperbody, and applying
libraries such as DLib and OpenPose, the position of facial feature and skeleton
of the child are extracted and can be used to obtain: head gaze, gaze and
gestures such as pointing. All these inputs can be combined to provide the robot
with more social inputs to test the sociability of a robotic controller and its
impact on the interaction.

The robot's location is obtained by displaying fiducial markers on the
touchscreen before the start of the interaction, so the transformation between
the robot coordinate system and the touchscreen is known. And this robot
location can also be used to identify gazes from the child to the robot.

To make the children believe the robot is moving objects on the touchscreen, we
synchronise a moving pointing gesture of the robot and a series of fake touches
appied on the screen, moving the desired object. Once an object and a goal
position have been selected, a planner generate a path for this image using the
A\mbox{*} algorithm on an occupancy map obtained with the items footprints, then
this plan is sent to a nodes synchronising the actuation on the robot and the
fake touches on the game.

@@

\paragraph{Wizard-of-Oz} To allow an experimenter to control the robot, a GUI to control the robot is
provided and presents an identical representation of the state of the game on an
other application which can be used on a tablet for example. The wizard can drag
the objects in a similar fashion as what the child would do on the Sandtray, and
on the release, the robot executes the dragging motion on the Sandtray, moving
an object to a new location. The source code can easily modify to add new
specific buttons to execute other actions, such as having the robot talk to the
child.

@@

A web interface can be used by the experimenter to manage the meta parameters of
the interaction: log data on the subjects, start-stop, select a task, manage data recording...

>>>>

\subsection{Interactive game} The interactive game
(Fig.~\ref{fig|architecture}.1) is coded using QML, and displays a main
background image on top of which items (animals, humans and objects) can be
moved.  The children can also use a drawing mode to create coloured strokes on a
layer between the background and the items, which adds another layer of
unconstrained interaction to the game (eg. Figure~\ref{fig|sandbox}. The game
exposes the image of the background, the drawings, and the positions of the
objects as a TF frame.

\subsection{Sensors} Two RGB-D cameras are mounted at fixed positions on the
Sandtray frame, each facing a child. This fixed position of the cameras allows
the extraction of social features such as head pose, eye gaze, pointing and body
posture, all described in a general coordinate system available to each software
node. In addition to the image, the cameras posses a microphone to record the
auditory aspect of the interaction. One node per camera
(Fig.~\ref{fig|architecture}.2) outputs on dedicated topics the audio and video
streams.

@@

\subsection{Robot Control} As stated in section~\ref{ssec|CRI}, a robot
(Fig.~\ref{fig|architecture}.9) can act as play partner instead of one of the
children. This robot can either be autonomous selecting actions based on the
inputs provided by the sensors and the game or be controlled by a human in a
Wizard of Oz fashion.

\paragraph{Autonomous} The current implementation exposes a large number of
information on the game and the state of the child that can be used in the robot
controller. The position of every item is exposed as a TF frame, the background
is segmented in zones of identical colors (Fig.~\ref{fig|architecture}.5),
social element of the state the interaction are collected through the RGBD
camera and the microphone facing the child. As visible on
Figures~\ref{fig|freeplay} and~\ref{fig|rviz}, the camera covers the head of the
child as well as most of the upperbody, and applying libraries such as DLib and
OpenPose, the position of facial feature and skeleton of the child are extracted
and can be used to obtain: head gaze, gaze and gestures such as pointing. All
these inputs can be combined to provide the robot with more social inputs to
test the sociability of a robotic controller (Fig.~\ref{fig|architecture}.3) and
its impact on the interaction.

The robot's location is obtained by displaying fiducial markers on the
touchscreen before the start of the interaction, so the transformation between
the robot coordinate system and the touchscreen is known
(Fig.~\ref{fig|architecture}.13). And this robot location can also be used to
identify gazes from the child to the robot.

To make the children believe the robot is moving objects on the touchscreen, we
synchronise a moving pointing gesture of the robot
(Fig.~\ref{fig|architecture}.4) and a series of fake touches
(Fig.~\ref{fig|architecture}.8) appied on the screen, moving the desired object.
Once an object and a goal position have been selected, a planner
(Fig.~\ref{fig|architecture}.6) generate a path for this image using the
A\mbox{*} algorithm on an occupancy map obtained with the items footprints, then
this plan is sent to a nodes synchronising the actuation on the robot and the
fake touches on the game.

@@

\paragraph{Wizard-of-Oz} To allow an experimenter to control the robot, a GUI to
control the robot (Fig.~\ref{fig|architecture}.11) is provided and presents an
identical representation of the state of the game on an other application which
can be used on a tablet for example. The wizard can drag the objects in a
similar fashion as what the child would do on the Sandtray, and on the release,
the robot executes the dragging motion on the Sandtray, moving an object to a
new location. The source code can easily modify to add new specific buttons to
execute other actions, such as having the robot talk to the child.

@@

A web interface (Fig.~\ref{fig|architecture}.10) can be used by the experimenter
to manage the meta parameters of the interaction: log data on the subjects,
start-stop, select a task, manage data recording...
